% CV template
%
% Author: Christopher Keyes
% Updated: September 24, 2021
%
% OK to use and edit!

\documentclass{cv_style}
\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{amsmath}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor = blue, citecolor = blue, anchorcolor = blue]{hyperref}

\begin{document}

	\footnotetext[1]{Updated \today}
    \pagenumbering{gobble}

    \begin{center} \name{Matthew Nicoletti} 

    \contact{Massachusetts Institute of Technology}{Department of Mathematics}{\text{}}{\href{mailto:mnicolet@mit.edu}{mnicolet@mit.edu}}{\text{}}
    
	\end{center}
	
	\section{Academic Interests}
	Broadly: Probability theory, algebraic combinatorics, mathematical physics, representation theory. Areas of focus: integrable models in statistical mechanics, stochastic dynamics, conformal invariance of critical lattice models.

	\section{Education}
		\subsection{Massachusetts Institute of Technology}
				\begin{itemize}
					\item Ph.D., Mathematics (expected graduation: 2024).
					\vspace{-2mm}
					\item Advisor: Alexei Borodin.
				\end{itemize}
				
		\subsection{UC Berkeley}
				\begin{itemize}
					\item B.A. Mathematics (honors program), Computer Science (2019).
					\vspace{-2mm}
					\item Senior thesis: {\em Limit Shapes of Lecture Hall Tableaux}.
					\vspace{-2mm}
					\item Senior Thesis Advisor: N. Reshetikhin.
					\vspace{-2mm}
					\item Awarded Dorothea Klumpke Roberts Prize in Mathematics (2019).
				\end{itemize}
		
% \paper[Collaborator's name]{Title}{Status (e.g.\ in prep., submitted, accepted)}{(links)}

	\section{Publications and Preprints}
		\begin{enumerate}			
					\item \paper[Leonid Petrov]{Irreversible Markov Dynamics and Hydrodynamics for KPZ States in the Stochastic Six Vertex Model}{Submitted to Annals of Probability (2022)}{\href{https://arxiv.org/abs/2201.12497}{arXiv:2201.12497}}
					\item \paper[Sylvie Corteel, David Keating]{Arctic Curves Phenomena for Bounded Lecture Hall Tableaux}{Communications in Mathematical Physics, 382, 1449-1493 (2021)}{\href{https://arxiv.org/abs/1905.02881}{arXiv:1905.02881}}
					
		\end{enumerate}
		
% \talk{title}{venue}{host}{date}
		
	\section{Talks}
		\begin{enumerate}
			\item \talk{Surface Growth and the Six Vertex Model}{Cornell University}{Cornell Probability Seminar}{Sep 19, 2022}
			\item \talk{Irreversible Markov Dynamics and Hydrodynamics for KPZ Phase in the Stochastic Six Vertex Model}{University of Vienna}{Vienna Probability Seminar}{Mar 2, 2022}
			\item \talk{Irreversible Markov Dynamics and Hydrodynamics for KPZ Phase in the Stochastic Six Vertex Model}{Stanford}{Solvable Lattice Models Seminar}{Mar 1, 2022}
			\item \talk{Irreversible Markov Dynamics and Hydrodynamics for KPZ Phase in the Stochastic Six Vertex Model}{MIT}{Integrable Probability Seminar}{Dec 3rd, 2021}
			\item \talk{Competitive erosion: limit shape and fluctuations}{MIT}{PUMAGRASS (Pure Math Graduate Student Seminar)}{Mar 26th, 2021}
		\end{enumerate}
		
	\section{Teaching Experience}
		\subsection{MIT}
		\begin{itemize}
		\item Teaching Assistant, Probability and Random Variables (course number 18.600, Fall 2022).
			\item Teaching Assistant, Complex Variables with Applications (course number 18.04, Spring 2022).
			\item Teaching Assistant, Linear Algebra (course number 18.06, Fall 2021).
			\item Teaching Assistant, Stochastic Calculus (course number 18.676, Spring 2021).
			\item Teaching Assistant, Probability Theory (course number 18.675, Fall 2020).
			\item Mentor for Undergraduate Research Project (MIT UROP+). Project: ``Laws of Large Numbers for Eigenvalue Distributions Using Bessel Generating Functions". Student: Andrew Yao
		\end{itemize}
				
	
\end{document}
